The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-09 paper.tex
update

  We do not simulate the spectral evolution of the CR, and we neglected the cooling and heating processes of CRs,\
  such as energy losses due to synchrotron and inverse Compton emission, and reacceleration in shocks.\

@@

@@

  \subsection{X-ray}
  \label{X-ray}
  The X-ray emissivity is computed\
  for each computational volume cell
  using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
  implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\
  The X-ray intensity map are then generated by projecting the emissivities\
  along lines of sight\
  pointing away from the solar position at $(x,y,z)=(8,0,0)$ kpc\
  with angular resolutions of 0.5 degrees\

@@

  \Cref{fig__xray_0.8keV_angle_000} shows\
  the comparison between simulated (top) and observed (bottom) all-sky map\
  in the range 0.6 -- 1.0 keV at the present time.\
  In the simulated map, the red arrow at the center of map represents the direction of the bipolar jet,\
  constantly ejecting at an angle of $45\circ$ to the disc normal in 1.2 Myr.

% 1. The boundary of eROSITA bubbles is a shock
% 2. North Polar Spur is not shown as it is a supernova remanent near us.
% 3. Why the innermost bubbles does not appear?
  The innermost bubbles, even though high density, is invisible in the simulated X-ray map as\
  the temperature of innermost bubbles is around $1$ -- $10$ eV\
  (see the temperature slice in \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}).\
  Consequently, the X-ray emission within the innermost bubbles
  is severely suppressed by the cutoff $\exp\left[-h\nu/k_{B}T\right]$ in thermal Bremsstrahlung emissivity.

@@

@@

>>>>

  We do not simulate the spectral evolution of the CR, and we neglected the cooling and heating processes of CRs,\
  such as energy losses due to synchrotron and inverse Compton emission, and reacceleration in shocks/turbulences.\

@@

 % the innermost bubbles is a reverse shock
 % the forward shock

@@

  \subsection{X-ray}
  \label{X-ray}
  The X-ray emissivity is computed\
  for each computational volume cell
  using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
  implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\
  The X-ray intensity map are then generated by projecting the emissivities\
  along lines of sight\
  pointing away from the solar position at $(R_{\odot},0,0)=(8,0,0)$ kpc\
  with angular resolutions of 0.5 degrees\

@@

  \Cref{fig__xray_0.8keV_angle_000} shows\
  the comparison between simulated (top) and observed (bottom) all-sky map\
  in the range 0.6 -- 1.0 keV at the present time.\
  In the simulated map, the red arrow at the center of map represents the direction of the bipolar jet,\
  constantly ejecting at an angle of $45^{\circ}$ to the disc normal in 1.2 Myr.

  \Cref{fig__x-ray-profile-0.8keV-000} displays the simulated count rate profiles (red)\
  in the same energy band as \Cref{fig__xray_0.8keV_angle_000}\
  cut at various galactic latitudes (as labelled), compared with the observation (black).\

  \Cref{fig_xray-map} is quite revealing in several ways.\
  First, the symmetric eROSITA bubbles can be formed by an inclined jet within a thin disk\
  of dense interstellar medium.\

  Second, as shown in \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp},\
  the half-width of the outermost bubbles is around 7 kpc,\
  corresponding to an half angular width $\sin^{-1}(7 \text{ kpc}/R_{\odot})\sim122^{\circ}$,\
  which is as wide as the eROSITA bubbles in the simulated X-ray map (top panel in \Cref{fig__xray_0.8keV_angle_000}).\
  We therefore suggest that the nature of eROSITA bubbles is indeed a forward shock\
  propagating through the halo gas, as previously proposed by \citet{Predehl2020}.

% 2. North Polar Spur is not shown as it is a supernova remanent near us.
  Third, the innermost bubbles, even though with high column density, is invisible in the simulated X-ray map as\
  the temperature of innermost bubbles is around $1$ -- $10$ eV\
  (see the temperature slice in \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}).\
  Consequently, the X-ray emission within the innermost bubbles
  is severely suppressed by the cutoff $\exp\left[-h\nu/k_{B}T\right]$ in thermal Bremsstrahlung emissivity.\
  This is the reason why the innermost bubbles is unseen in the observation.

@@

 We close on a speculative note that predicts an existence of a third bubbles for
 future observations.

@@

We therefore suggest that the Fermi bubbles and the eROSITA structure are physically related,\
as suggested by \citet{Predehl2020}.

Our discovery confirms the previously suggested common origin of the two objects \citep{Sofue2000,Kataoka2018}
